---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# FARSpackageLCP

FARSpackageLCP implements five useful functions to process and analyze data from the **Fatality Analysis Reporting System (FARS)**. The functions are the following:

1. *fars_read*: A read data file function.
2. *make_filename*: A simple function to create the filename of accident data for a given year.
3. *fars_read_years*: A function to extraxct monthly data from a given set of years.
4. *fars_summarize_years*: A function to summarize FARS events per month and year.
5. *fars_map_state*: A function to create a map of FARS events and points plota for a given a state number and year.

# Details
The R package BuildinganRPackageLCP has the following main goals:

* Manage FRS data file names from user provided year(s).

* Extract and summarize FARS data from user provided year(s).

* Map FARS data per state and user provided year.


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```
